---
title: "In Class Lab - DIY Functions"
author: "Quang Le"
date: "DATA 2401"
output: html_document
---
**Note: Your exam will be in a similar format to this (RMarkdown File with Questions and Code chunks for your answers), so make sure you have the process for knitting to html working.** 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In Class Activity 
The questions from your notes today are below, please copy your answers them here! Then complete the two new tasks, and attempt the "hard mode" if you have time. 

1. Write your own function that takes the temperature in Fahrenheit as an argument and returns the Celsius equivalent. 

```{R}
# Function to convert Fahrenheit to Celsius
fahrenheit_to_celsius <- function(fahrenheit) {
  celsius <- (fahrenheit - 32) * 5/9
  return(celsius)
}
fahrenheit_to_celsius(212)
```

2. Expand that function so that it takes a temperature in Fahrenheit and a distance in feet and returns **both** the temperature in Celcius and the distance in meters (you'll likely need to remember the `c()` function!)


```{r}
# Expanded function to convert Fahrenheit to Celsius and feet to meters
convert_temp_and_distance <- function(fahrenheit, feet) {
  celsius <- (fahrenheit - 32) * 5/9
  meters <- feet * 0.3048
  return(c(celsius, meters))
}
convert_temp_and_distance(212,100)

```


3. Write a function that prints out a statement of whether the number passed as an argument is positive, negative or 0. 

```{R}
# Function to check if a number is positive, negative, or zero
check_number <- function(number) {
  if (number > 0) {
    print("The number is positive.")
  } else if (number < 0) {
    print("The number is negative.")
  } else {
    print("The number is zero.")
  }
}
check_number(5)

```

4. Write a function that returns the absolute value of the number passed as an argument.
   + Don't use `abs()`. Use the flow from problem 1 and multiply by negative one as necessary. 
   
```{r}
# Function to return the absolute value of a number
my_abs <- function(number) {
  if (number < 0) {
    number <- number * -1
  }
  return(number)
}
my_abs(-7)

```

5. Hard mode: add an error check to that function that prints out the string "Please pass a numerical value to this function" if the user passes the function a string. 
   + There are functions that check and return T/F: `is.numeric()` or `is.character()` would be relevant here
   
```{r}
# Function to return the absolute value with error check
my_abs_with_check <- function(number) {
  if (!is.numeric(number)) {
    print("Please pass a numerical value to this function")
  } else {
    if (number < 0) {
      number <- number * -1
    }
    return(number)
  }
}
my_abs_with_check(!15)
```
   
   





```

